Closed-loop Neuromorphic Benchmarks

### 2015-11-13 paper/paper.tex
Added analysis of lego robot improvement

However, with adaptation (the right-hand side of Figure \ref{fig:ev3}),
the system learns to counteract this extra force due to gravity.  After
the first 5 seconds, the system is able to bring $q$ much closer to the
desired $q_d$.

@@

>>>>

However, with adaptation (the right-hand side of Figure \ref{fig:ev3}),
the system learns to counteract this extra force due to gravity.  After
the first 5 seconds, the system is able to bring $q$ much closer to the
desired $q_d$.  Figure \ref{fig:ev3runs} shows the average improvement over
50 experimental runs with different randomly-generated desired target paths
$q_d(t)$.  Adaptation provides a clear improvement.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=9cm]{figures/plot_ev3}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:ev3runs} Figure \arabic{figure}.}{ The effect
     of adaptive control on a single-joint lego robot (Figure \ref{fig:lego}).
     Each run uses a randomly generated desired trajectory $q_d(t)$ over
     20 seconds, and root-mean-squared-error is computed over the last
     10 seconds only.  The adaptive algorithm provides a significant improvement
     ($p<0.05$; two-tailed t-test; 50 samples).
     Scatterplots show individual runs (with random jitter on the x-axis
     to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.}
\end{figure}
